Truthfulness Verification System

### 2011-02-23 proposal/paper.tex
added example sections

>>>>

\subsubsection{Finding Sense using Wordnet}
To classify a statement as true or false we need to get the semantic of sense of the words of the sentences. For example consider the following sentence.

Now our query results from ontologies will give us the fact that Tom hanks is a male actor. Now using wordnet we will be able to find that actress means female actor. So by simple inference our system will be able to classify the above example as untruthful.

\subsubsection{Use of Co-reference Program}
Totha: please write up two lines here
